06-assessing_lime_explanations

### 2019-02-12 journals/06-assessing_lime_explanations.Rmd
updated journal 06 and removed caching

---
title: "06-assessing_lime_explanations"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

@@

This journal compares the results from the different LIME implementations.

@@

# Accuracy

@@

# Consistency with One Implementation

@@

## Fleiss's Kappa

@@

## Tile Plots of Features Chosen

@@

## Attempts at Arranging the Tile Plots

@@

## Plot of Number of Features Chosen

@@

# Consistency Across Implementations

@@

@@

@@

@@

@@

```{r}
devtools::session_info()
```

>>>>

---
title: "06-assessing_lime_explanations"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

@@

This journal visualizes and compares the results from the different LIME implementations.

@@

# One Implementation

## Accuracy

@@

## Consistency

@@

### Fleiss's Kappa

@@

### Tile Plots of Features Chosen

@@

### Attempts at Arranging the Tile Plots

@@

### Plot of Number of Features Chosen

@@

# Multiple Implementations

## Accuracy

@@

### Comparing MSE and $R^2$

@@

## Consistency

### Plots of Number of Features Chosen

@@

### Fleiss's Kappa

@@

### Tile Plots of Features Chosen

@@

```{r}
sessionInfo()
```
